Labour Market Resilience

### 2024-03-12 outputs/paper/paper.qmd
update paper and data

data <- read.csv(here::here("inputs/data/Cleaned_Data.csv"))
# Get rid of the first letter X for each of the years
colnames(data)[1] <- "work_hours"
colnames(data) <- gsub("X", "", colnames(data))

@@

>>>>

data <- read.csv(here::here("inputs/data/cleaned_data.csv"))
# Get rid of the first letter X for each of the years
colnames(data)[1] <- "work_hours"
colnames(data) <- gsub("X", "", colnames(data))

@@

## Survey Introduction
The supplemental survey is available here: [Google Form Link](https://forms.gle/Ffma5ggEcP6wfumu6)
